---
title: 'Peer-graded Assignment: Sniny & RMarkdown'
author: "Ana Real"
date: "April 24, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Personal savings per country

In this work you can see the most important variable related to personal savings on people from 50 countries.

```{r tab, message=FALSE, warning=FALSE}
library(knitr)
kable(head(data.frame("country"=rownames(LifeCycleSavings),LifeCycleSavings)))
```

## App

In the application you are able to understand the variables behind the **sr** personal savings variable.

```{r plot, message=FALSE, warning=FALSE}
library(ggplot2)
library(reshape2)
data <- melt(LifeCycleSavings, id.vars="sr", value.name = "predictors")
ggplot(data, aes(x=sr, y=predictors, col=variable)) + geom_point()
```

## Example

Select one predictor and get the plot with the regression line.

```{r plot2, message=FALSE, warning=FALSE}
model1 <- lm(sr ~ pop15, data = LifeCycleSavings)
plot(LifeCycleSavings$sr, LifeCycleSavings$pop15, xlab = "Personal Savings", 
                 ylab = "Numeric % of population under 15", bty = "n", pch = 16,
                 xlim = c(0,21), ylim = c(0,45))
            abline(model1, col = "purple", lwd = 2)
```

## Summary

Get an easy summary of the predictor choosen in the last tab.

```{r box}
boxplot(LifeCycleSavings$pop15, main = "Numeric % population under 15")
```
